### 2014-10-28 LongDataResearchNotes/ARModel.Rmd
Results are in with both the by hour and by day within hour AR stucture.

So the action goes away.  Lets assume AR structure is with previous hour and not previous day.  This will take a while to run.  There are a lot of parameters.
```{r}
summary(gls(HE~hour+(F+LagHE+Weather+LagWeather):hour, data=LagFormData,corAR1(form=~1),na.action=na.omit))
```

FULL WIN.  It works.

>>>>

So the action goes away.  Lets assume AR structure is with previous previous day within hour.  This will take a while to run.  There are a lot of parameters.

```{r}
LagFormData<-sqldf("select * from LagFormData order by hour, DateOnly;")

summary(gls(HE~hour+(F+LagHE+Weather+LagWeather):hour, data=LagFormData,corAR1(form=~1),na.action=na.omit))
```
Sweet works except hours 1-5

Now go by hour within day

```{r}
LagFormData<-sqldf("select * from LagFormData order by DateOnly,hour;")
summary(gls(HE~hour+(F+LagHE+Weather+LagWeather):hour, data=LagFormData,corAR1(form=~1),na.action=na.omit))
```

and the results are different.  Now we have to figure out which is right, or perhaps both.
